Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-10-30 Talks/FU-Berlin/talk-part-1.tex
update of talk

\begin{frame}{Introduction} \small
\begin{minipage}{.56\textwidth} 
\includegraphics[width=\textwidth]{spiegel1} 
\vskip1em
Germany \\
- Telepolis \& Heise \\
- Spiegel Online \\
- FAZ \\
- Die Welt \\
- Berliner Morgenpost \\
- Hamburger Abendpost \\
- \ldots \\
\end{minipage} \hfill
%
\begin{minipage}{.3\textwidth}
Austria \\
- Die Presse \\
- Wiener Zeitung \\
- ORF \\
- \ldots \\

Italy \\
- Repubblica \\
- Today.it \\
- Ilsussidario \\
- \ldots \\

@@

International \\
- Spiegel International \\
- Yahoo Finance \\
- CNET \\
- United Press Intl. \\
- \ldots
\end{minipage}
\end{frame}

@@

\begin{frame}{Introduction} \large
Main challenge: \hfill No provers for \emph{Higher-order Modal Logic} \textcolor{red}{HML} \\[1em]

Our idea: \hfill Embedding in \emph{Higher-order Classical Logic} \textcolor{blue}{HOL} \\
\,\hfill {\small [Benzm\"ullerPaulson, Logica Universalis, 2013]} \\[2em]

@@

\begin{itemize}
\item[A:] pen and paper: detailed natural deduction proof 
\item[B:] formalization: axioms, defs, thms  in \textcolor{blue}{HOL}
\item[] proof automation: theorems provers \textsc{Leo-II} and \textsc{Satallax} 
\item[] consistency: automatic verification with \textsc{Nitpick} 
\item[C:] step-by-step verification: proof assistant \textsc{Coq} 
\item[D:] automation \& verification: proof assistant 
  \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
Did we get new results? \hfill  \textcolor{red}{Yes --- let's discuss later!}
\end{frame}

>>>>

\begin{frame}{} \small
\vskip1em
\begin{minipage}{.56\textwidth} 
\colorbox{gray}{\includegraphics[width=\textwidth]{spiegel1}} 
\vskip1em
Germany \\
- Telepolis \& Heise \\
- Spiegel Online \\
- FAZ \\
- Die Welt \\
- Berliner Morgenpost \\
- Hamburger Abendpost \\
- \ldots \\
\end{minipage} \hfill
%
\begin{minipage}{.3\textwidth}
Austria \\
- Die Presse \\
- Wiener Zeitung \\
- ORF \\
- \ldots \\

Italy \\
- Repubblica \\
- Ilsussidario \\
- \ldots \\

@@

US \\
- ABC News \\
- \ldots \\

International \\
- Spiegel International \\
- Yahoo Finance \\
% - CNET \\
- United Press Intl. \\
- \ldots \\
\end{minipage}
\end{frame}

\begin{frame}{Introduction --- Quick answers to your most pressing questions!} \large
\colorbox{gray}{\includegraphics[width=\textwidth]{MacBookGrab}} 
\pause
\vfill
Are we in contact with Steve Jobs? \hfill No \\[2em]
Do you really need a MacBook to obtain the results? \hfill No \\[2em]
Is Apple sending us money? \hfill No \\
\, \hfill (but maybe they should)
\end{frame}

@@

\begin{frame}{Introduction} \large
Main challenge: \hfill No provers for \emph{Higher-order Modal Logic\/} (\textcolor{red}{HML}) \\[1em]

Our solution: \hfill Embedding in \emph{Higher-order Classical Logic\/} (\textcolor{blue}{HOL}) \\
\,\hfill {\small [Benzm\"ullerPaulson, Logica Universalis, 2013]} \\[2em]

@@

\begin{itemize}
\item[A:] pen and paper: detailed natural deduction proof 
\item[B:] formalization: in classical higher-order logic (\textcolor{blue}{HOL})
\item[] proof automation: theorem provers \textsc{Leo-II} and \textsc{Satallax} 
\item[] consistency: model finder \textsc{Nitpick (Nitrox)} 
\item[C:] step-by-step verification: proof assistant \textsc{Coq} 
\item[D:] automation \& verification: proof assistant 
  \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
Did we get new results? \hfill  \textcolor{red}{Yes --- let's discuss later!}
\end{frame}
